Global study of well-being and internet adoption | Online analysis supplement

### 2021-11-19 03-analysis.Rmd
Edits

# MCMC settings
options(brms.backend = "cmdstanr")
hmc <- list(
  chains = 6,
  cores = 6,
  threads = 2,
  iter = 300, 
  warmup = 200,
  refresh = 10,
  adapt_delta = .9, 
  max_treedepth = 10
)

@@

All the outcome variables are proportions (0-1) at this point. This creates problems with the HMC because the self-harm rates are so low. HMC works better with variables roughly on the unit scale.

@@

# Important: do this for both val AND se
# Multiply by 1000
dat <- dat %>% 
  group_by(cause) %>% 
  mutate(across(val:se, ~.x*1000)) %>% 
  ungroup()

dat %>%
  group_by(cause) %>%
  summarise(median = median(val), min = min(val), max = max(val))

# # It is then easy to back-transform
# dat %>% 
#   left_join(dat_scales) %>% 
#   group_by(cause) %>% 
#   mutate(
#     val = rescale(val, to = c(unique(min), unique(max))),
#     se = rescale(val, to = c(unique(min), unique(max)))
#   ) %>% 
#   summarise(median = median(val), min = min(val), max = max(val))
```

@@

```{r}
fit_1b <- brm(
  bf_itu + bf_1b + set_rescor(FALSE),
  data = filter(dat, cause == "Anxiety"),
  chains = 0,
  threads = hmc$threads,
  file = "output/brm-1b"
)

@@

fit_1c <- brm(
  bf_itu + bf_1c + set_rescor(FALSE),
  data = filter(dat, cause == "Anxiety"),
  chains = 0,
  threads = hmc$threads,
  file = "output/brm-1c"
)

fits_1c <- dat %>%
  group_by(cause) %>% 
  summarise(
    fit = list(
      update(
        fit_1c, 
        newdata = cur_data_all(),
        chains = hmc$chains, cores = hmc$cores, threads = hmc$threads,
        iter = hmc$iter, warmup = hmc$warmup, refresh = hmc$refresh,
        control = list(
          adapt_delta = hmc$adapt_delta, 
          max_treedepth = hmc$max_treedepth
        ),
        file = str_glue("output/brm-1c-{cur_group()}")
      )
    )
  )

@@

```{r}
pp_check(
  fits_1c$fit[[1]], 
  ndraws = 30, 
  resp = "internet", 
  newdata = fits_1c$fit[[1]]$data
  )

pp_check(
  fits_1c$fit[[1]], 
  ndraws = 10, 
  type = "dens_overlay_grouped",
  group = "region",
  resp = "val", 
  newdata = fits_1c$fit[[1]]$data
)
```

@@

```{r}
fits_1 <- reduce(
  list(
    fits_1a %>% rename(fit_1a = fit), 
    fits_1b %>% rename(fit_1b = fit),
    fits_1c %>% rename(fit_1c = fit)
  ), 
  left_join
) %>% 
  pivot_longer(fit_1a:fit_1c, names_to = "model", values_to = "fit")
fits_1 %>% 
  mutate(
    out = map(
      fit, 
      ~as_draws_df(.x, variable = "^b_", regex = TRUE) %>% 
        summarise_draws(
          mean, quantile, rhat, 
          .args = list(probs = c(.025, .975))
        )
    )
  ) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  mutate(across(where(is.numeric), ~round(., 2))) %>% 
  mutate(
    result = str_glue(
      "{mean} ({`2.5%`}, {`97.5%`}) [rh = {round(rhat, 1)}]"
    )
  ) %>% 
  select(-c(mean, `2.5%`, `97.5%`, rhat)) %>% 
  pivot_wider(names_from = model, values_from = result) %>% 
  kbl() %>% 
  kable_paper(html_font = Font)
```

@@

```{r}
tmp_coefs <- fits_1c %>% 
  mutate(
    out = map(
      fit, 
      ~hypothesis(
        .x, 
        # Rescale coefficient here to years on %
        c(str_glue("val_year = 0")),
        scope = "coef",
        group = "region"
      )$hypothesis
    )
  ) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  mutate(across(where(is.numeric), ~round(., 2))) %>% 
  mutate(result = str_glue('**{Estimate}** [{CI.Lower}, {CI.Upper}]')) %>% 
  select(cause, region = Group, result)
tmp_coefs
pseudo_gwp <-
  bind_rows(
    distinct(gbd, region, year, val = NA) %>% 
      crossing(
        cause = fct_inorder(
          c(
            "Negative\nexperiences", 
            "Positive\nexperiences", 
            "Life\nsatisfaction"
          )
        )
      )
  )

@@

# Draw small multiples figure, outcomes x regions
dat_all %>% 
  mutate(year = make_date(year)) %>% 
  ggplot(aes(year, mean)) +
  scale_y_continuous(
    "Value",
    labels = function(x) percent(x, .01) %>% str_remove("\\.00"),
    breaks = pretty_breaks()
  ) +
  scale_x_date(
    "Year",
    breaks = make_date(c(2000, 2005, 2010, 2015)), 
    date_labels = "'%y", 
    expand = expansion(.02)
  ) +
  geom_line(
    aes(group = interaction(country, cause)), 
    alpha = .25, size = .4, color = "dodgerblue1"
  ) +
  stat_summary(
    fun = mean, geom = "line", 
    size = .6, color = "dodgerblue4"
  ) +
  facet_grid(cause~region, scales = "free_y") +
  theme(
    legend.position = "none",
    panel.spacing = unit(3, "pt")
  ) +
  geom_richtext(
    data = tmp_coefs %>% mutate(cause = fct_inorder(str_to_title(cause))),
    aes(x = make_date(2000), y = Inf, label = result),
    size = 2.4, vjust = .9, hjust = 0.05, color = "dodgerblue4",
    family = Font,
    fill = NA, label.color = NA
  )
```

@@

```{r}
bf_2b <- bf(
  val | resp_se(se, sigma = TRUE) ~ 
    year + sex + age + i1_cw + i1_cb +
    (year + sex + age + i1_cw | country) +
    (year + sex + age + i1_cw | region),
  family = gaussian()
)
fit_2b <- brm(
  bf_2b,
  data = filter(dat, cause == "Anxiety"),
  chains = 0,
  threads = hmc$threads,
  file = "output/brm-2b"
)
fits_2b <- dat %>% 
  group_by(cause) %>% 
  summarise(
    fit = list(
      update(
        fit_2b, 
        newdata = cur_data_all(),
        chains = hmc$chains, cores = hmc$cores, threads = hmc$threads,
        iter = hmc$iter, warmup = hmc$warmup, refresh = hmc$refresh,
        control = list(
          adapt_delta = hmc$adapt_delta, 
          max_treedepth = hmc$max_treedepth
        ),
        file = str_glue("output/brm-2b-{cur_group()}")
      )
    )
  )

@@

fit_2c <- brm(
  bf_2c,
  data = filter(dat, cause == "Anxiety"),
  chains = 0,
  threads = hmc$threads,
  file = "output/brm-2c"
)

fits_2c <- dat %>% 
  group_by(cause) %>% 
  summarise(
    fit = list(
      update(
        fit_2c, 
        newdata = cur_data_all(),
        chains = hmc$chains, cores = hmc$cores, threads = hmc$threads,
        iter = hmc$iter, warmup = hmc$warmup,
        control = list(adapt_delta = hmc$d, max_treedepth = hmc$m),
        file = str_glue("output/brm-2c-{cur_group()}")
      )
    )
  )
```

@@

```{r}
fits_2c <- tibble(
  cause = c("Anxiety", "Depression"),
  fit = list(read_rds("output/brm-2c-Anxiety.rds"), read_rds("output/brm-2c-Depression.rds"))
)
f2d <- fits_2c %>% 
  mutate(
    out = 
      map(
        fit, 
        ~as_draws_df(., variable = "^b_|^sd_", regex = TRUE) %>% 
          summarise_draws(samples = length, default_convergence_measures())
        )
    ) %>% 
  select(-fit) %>% 
  unnest(out)
f2d %>%  
  kbl(
    caption = "HMC Diagnostics, Model 2c",
    digits = c(0,0,0,2,0,0)
  ) %>% 
  kable_paper(html_font = Font, full_width = FALSE) %>% 
  column_spec(
    4, 
    color = "white",
    background = spec_color(
      f2d$rhat, 
      direction = 1, 
      option = "C", 
      end = .7
    )
  ) %>% 
  scroll_box(height = "600px", width = "800px")
```

@@

```{r}
fits_2c %>% 
  mutate(
    out = map(
      fit, 
      ~as_draws_df(.x, variable = "^b_", regex = TRUE) %>% 
        summarise_draws(
          mean, quantile, rhat, 
          .args = list(probs = c(.025, .975))
        )
    )
  ) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  mutate(across(where(is.numeric), ~round(., 2))) %>% 
  mutate(
    result = str_glue(
      "b = {mean} ({`2.5%`}, {`97.5%`})"
    )
  ) %>% 
  select(-c(mean, `2.5%`, `97.5%`, rhat)) %>% 
  pivot_wider(names_from = cause, values_from = result) %>% 
  kbl() %>% 
  kable_paper(html_font = Font)
```

@@

```{r}
anx_draws <- spread_draws(
  fit_anx, 
  b_i1_cw, r_region[region, term] | region
) %>% 
  filter(term == "i1_cw") %>% 
  ungroup() %>% 
  select(-term) %>% 
  rename(Average = b_i1_cw) %>% 
  mutate(outcome = "Anxiety")
dep_draws <- spread_draws(
  fit_dep, 
  b_i1_cw, r_region[region, term] | region
) %>% 
  filter(term == "i1_cw") %>% 
  ungroup() %>% 
  select(-term) %>% 
  rename(Average = b_i1_cw) %>% 
  mutate(outcome = "Depression")
sel_draws <- spread_draws(
  fit_sel, 
  b_i1_cw, r_region[region, term] | region
) %>% 
  filter(term == "i1_cw") %>% 
  ungroup() %>% 
  select(-term) %>% 
  rename(Average = b_i1_cw) %>% 
  mutate(outcome = "Selfharm")

results_text <- bind_rows(anx_draws, dep_draws, sel_draws) %>% 
  group_by(outcome) %>% 
  summarise(parameters(cur_data()[-c(1:3)])) %>% 
  mutate(region = str_replace(Parameter, "\\.", " ")) %>% 
  mutate(is_average = region == "Average") %>% 
  mutate(region = if_else(region=="Average", "**Average**", region)) %>% 
  mutate(across(Median:CI_high, ~format(round(., 2), nsmall = 2)))

p_internet_main_coefs <- bind_rows(anx_draws, dep_draws, sel_draws) %>% 
  mutate(across(Africa:Southern.Asia, ~.+Average)) %>% 
  pivot_longer(Average:Southern.Asia, names_to = "region") %>% 
  mutate(region = fct_relevel(factor(region), "Average")) %>% 
  mutate(outcome = factor(outcome)) %>% 
  mutate(is_average = region == "Average") %>% 
  mutate(region = str_replace(region, "\\.", " ")) %>% 
  mutate(region = if_else(region=="Average", "**Average**", region)) %>% 
  ggplot(aes(value, region, fill = is_average, alpha = is_average)) +
  scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
  scale_alpha_manual(values = c(.4, .8)) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  scale_shape_manual(values = c(21, 19)) +
  scale_y_discrete(expand = expansion(c(0.01, .1))) +
  scale_x_continuous(
    "Magnitude of association between internet adoption and well-being", 
    breaks = pretty_breaks(), 
    expand = expansion(c(.1, .5))
  ) +
  stat_halfeye(
    point_interval = NULL, normalize = "panels", 
    height = .75, adjust = 1.5
  ) +
  stat_pointinterval(
    alpha = 1, .width = c(.9),
    interval_size = .5,
    point_size = 1.5,
    fill = "white",
    aes(shape = after_stat(xmin > 0 | xmax < 0)),
    position = position_nudge(0, -.025)
  ) +
  geom_text(
    data = results_text, alpha = 1, size = 2.75, hjust = 1, vjust = -0.2,
    aes(
      x = Inf, 
      label = str_glue("{Median} [{CI_low}, {CI_high}]")
    )
  ) +
  facet_wrap("outcome", nrow = 1, scales = "free_x") +
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_markdown(),
    legend.position = "none"
  )

(wrap_elements(grid::textGrob('Negative experiences\nTBD')) |
    wrap_elements(grid::textGrob('Positive experiences\nTBD')) |
    wrap_elements(grid::textGrob('Life satisfaction\nTBD'))) /
  p_internet_main_coefs
```

@@

```{r}
pred_data <- gbd_wide %>% 
  distinct(region, country, sex, age, i1_cb, i1_cw = 0, time = 0) %>% 
  filter(country %in% sort(unique(fit_anx$data$country)))

tmp <- epred_draws(
  fit_anx, pred_data, re_formula = 
    ~(1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region) + 
    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | country)
)

tmp %>% 
  group_by(region, country, i1_cb) %>% 
  summarise(mean(.epred))

conditional_effects(fit_anx, "i1_cb")

gbd_wide %>% 
  group_by(country) %>% 
  summarise(i1_cb = unique(i1_cb), anx = mean(Anxiety)) %>% 
  ggplot(aes(i1_cb, anx)) +
  geom_point() +
  stat_smooth()

filter(country %in% sort(unique(fit_anx$data$country))) %>% 
  mutate(time = 0) %>% 
  group_by(country) %>% 
  mutate(xmin = min(i1_cw, na.rm = TRUE), xmax = max(i1_cw, na.rm = TRUE)) %>% 
  filter(i1_cw %in% c(xmin, xmax)) %>% 
  ungroup()
```

@@

```{r}
# Get some stuff and transform :)
get_draws <- function(fit) {
  draws_region <- spread_draws(
    fit, 
    b_i1_cw, `b_age1:i1_cw`, `b_sex1:i1_cw`,
    r_region[region, term] | term
  ) %>% 
    mutate(
      `15 to 19` = b_i1_cw + i1_cw + (`age1:i1_cw` + `b_age1:i1_cw`)*-0.5,
      `20 to 24` = b_i1_cw + i1_cw + (`age1:i1_cw` + `b_age1:i1_cw`)*0.5,
      Female = b_i1_cw + i1_cw + (`sex1:i1_cw` + `b_sex1:i1_cw`)*-0.5,
      Male = b_i1_cw + i1_cw + (`sex1:i1_cw` + `b_sex1:i1_cw`)*0.5,
      Age = `age1:i1_cw` + `b_age1:i1_cw`,
      Sex = `sex1:i1_cw` + `b_sex1:i1_cw`
    ) %>% 
    select(region, `15 to 19`:Sex)

  draws_avg <- spread_draws(
    fit, 
    b_i1_cw, `b_age1:i1_cw`, `b_sex1:i1_cw`
  ) %>% 
    mutate(
      `15 to 19` = b_i1_cw + `b_age1:i1_cw`*-0.5,
      `20 to 24` = b_i1_cw + `b_age1:i1_cw`*0.5,
      Female = b_i1_cw + `b_sex1:i1_cw`*-0.5,
      Male = b_i1_cw + `b_sex1:i1_cw`*0.5,
      Age = `b_age1:i1_cw`,
      Sex = `b_sex1:i1_cw`
    ) %>% 
    mutate(region = "**Average**") %>% 
    select(region, `15 to 19`:Sex)

@@

draws <- bind_rows(
  "Anxiety" = get_draws(fit_anx),
  "Depression" = get_draws(fit_dep),
  "Selfharm" = get_draws(fit_sel),
  .id = "outcome"
)

draws_sum <- draws %>% 
  select(outcome, region, Age, Sex) %>% 
  group_by(outcome, region) %>% 
  summarise(
    describe_posterior(
      cur_data(), centrality = "mean", test = "pd"
    )
  ) %>% 
  rename(panel = Parameter) %>% 
  mutate(across(where(is.numeric), ~round(., 2)))

>>>>

# MCMC settings
options(brms.backend = "cmdstanr")
hmc <- list(
  chains = 6,
  cores = 6,
  threads = 2,
  iter = 1500, 
  warmup = 1000,
  refresh = 10,
  adapt_delta = .95, 
  max_treedepth = 11
)

@@

All the outcome variables are proportions (0-1) at this point. They need to be rescaled for HMC efficiency (self-harm models do not converge at this scale.) So remember to back-transform when interpreting results!

@@

# Important: do this for both val AND se
dat <- dat %>% 
  group_by(cause) %>% 
  mutate(across(val:se, ~.x*100)) %>% 
  ungroup()

dat %>%
  group_by(cause) %>%
  summarise(median = median(val), min = min(val), max = max(val))
```

@@

```{r eval = FALSE}
fit_1b <- brm(
  bf_itu + bf_1b + set_rescor(FALSE),
  data = filter(dat, cause == "Anxiety"),
  chains = 0,
  threads = hmc$threads,
  file = "output/brm-1b"
)

@@

# Regression coefficients
p <- prior(normal(0, .5), class = b, resp = val) +
  prior(normal(0, 1), class = b, coef = sex1, resp = val) +
  # Standard deviations
  prior(
    student_t(7, 0, .5), 
    class = sd, resp = val, group = region
  ) +
  prior(
    student_t(7, 0, 1.5), 
    class = sd, resp = val, group = region, coef = Intercept
  ) +
  prior(
    student_t(7, 0, .5), 
    class = sd, resp = val, group = country
  ) +
  prior(
    student_t(7, 0, 1.5), 
    class = sd, resp = val, group = country, coef = Intercept
  ) +
  # Correlations
  prior(lkj(2), class = cor, group = country) +
  prior(lkj(2), class = cor, group = region)

# Compile model separately for each outcome to give independent default priors
fits_1c <- dat %>%
  group_by(cause) %>% 
  summarise(
    fit = list(
      brm(
        formula = bf_itu + bf_1c + set_rescor(FALSE), 
        data = cur_data_all(),
        prior = p,
        sample_prior = "yes",
        chains = hmc$chains, 
        cores = hmc$cores, 
        threads = hmc$threads,
        iter = hmc$iter, 
        warmup = hmc$warmup, 
        refresh = hmc$refresh,
        control = list(
          adapt_delta = hmc$adapt_delta, 
          max_treedepth = hmc$max_treedepth
        ),
        file = str_glue("output/brm-1c-{cur_group()}")
      )
    )
  )

@@

```{r}
tmp <- fits_1c %>% 
  mutate(
    out = map(
      fit, 
      ~pp_check(
        .x, 
        ndraws = 10, 
        type = "dens_overlay_grouped",
        group = "region",
        resp = "val", 
        newdata = .x$data
      ) + facet_wrap("group", nrow = 1, scales = "free")
    )
  )
wrap_plots(tmp$out, nrow = 3) &
  scale_x_continuous(
    breaks = pretty_breaks(2),
    labels = function(x) percent(x/100)
  )
```

@@

```{r}
fits_1 %>% 
  mutate(
    out = map(
      fit, 
      ~as_draws_df(.x, variable = "^b_", regex = TRUE) %>% 
        summarise_draws(
          mean, quantile, rhat, 
          .args = list(probs = c(.025, .975))
        )
    )
  ) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  mutate(across(where(is.numeric), ~round(., 2))) %>% 
  mutate(
    result = str_glue(
      "{mean} ({`2.5%`}, {`97.5%`}) [rh = {round(rhat, 1)}]"
    )
  ) %>% 
  select(-c(mean, `2.5%`, `97.5%`, rhat)) %>% 
  pivot_wider(names_from = model, values_from = result) %>% 
  kbl() %>% 
  kable_paper(html_font = Font)
```

@@

```{r}
tmp_coefs <- fits_1c %>% 
  mutate(
    out = map(
      fit, 
      ~hypothesis(
        .x, 
        # Rescale coefficient here to years on %
        # Note self harm doesnt work now
        c(str_glue("val_year = 0")),
        scope = "coef",
        group = "region"
      )$hypothesis
    )
  ) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  mutate(across(where(is.numeric), ~round(., 2))) %>% 
  mutate(result = str_glue('**{Estimate}**<br>[{CI.Lower}, {CI.Upper}]')) %>% 
  select(cause, region = Group, result)
tmp_coefs
pseudo_gwp <-
  bind_rows(
    distinct(gbd, region, year, val = NA) %>% 
      crossing(
        cause = fct_inorder(
          c(
            "Negative\nexperiences", 
            "Positive\nexperiences", 
            "Life\nsatisfaction"
          )
        )
      )
  )

@@

# Draw small multiples figure, outcomes x regions
dat_all %>% 
  mutate(year = make_date(year)) %>% 
  ggplot(aes(year, mean)) +
  scale_y_continuous(
    "Value",
    labels = function(x) percent(x, .01) %>% str_remove("\\.00"),
    breaks = pretty_breaks()
  ) +
  scale_x_date(
    "Year",
    breaks = make_date(c(2000, 2005, 2010, 2015)), 
    date_labels = "'%y", 
    expand = expansion(.02)
  ) +
  geom_line(
    aes(group = interaction(country, cause)), 
    alpha = .25, size = .4, color = "dodgerblue1"
  ) +
  stat_summary(
    fun = mean, geom = "line", 
    size = .6, color = "dodgerblue4"
  ) +
  facet_grid(cause~region, scales = "free_y") +
  theme(
    legend.position = "none",
    panel.spacing = unit(3, "pt")
  ) +
  geom_richtext(
    data = tmp_coefs %>% mutate(cause = fct_inorder(str_to_title(cause))),
    aes(x = make_date(2000), y = Inf, label = result),
    size = 2.4, vjust = .9, hjust = 0.05, color = "black",
    family = Font,
    fill = NA, label.color = NA
  )
```

@@

```{r}
bf_2b <- bf(
  val | resp_se(se, sigma = TRUE) ~ 
    year + sex + age + i1_cw + i1_cb +
    (year + sex + age + i1_cw | country) +
    (year + sex + age + i1_cw | region),
  family = gaussian(), 
  unused = ~ cause # Save this variable in the data frame
)
fit_2b <- brm(
  bf_2b,
  data = filter(dat, cause == "Anxiety"),
  chains = 0,
  threads = hmc$threads,
  file = "output/brm-2b"
)
fits_2b <- dat %>% 
  group_by(cause) %>% 
  summarise(
    fit = list(
      update(
        fit_2b, 
        newdata = cur_data_all(),
        chains = hmc$chains, cores = hmc$cores, threads = hmc$threads,
        iter = hmc$iter, warmup = hmc$warmup, refresh = hmc$refresh,
        control = list(
          adapt_delta = hmc$adapt_delta, 
          max_treedepth = hmc$max_treedepth
        ),
        file = str_glue("output/brm-2b-{cur_group()}")
      )
    )
  )

@@

# Regression coefficients
p <- prior(normal(0, .5), class = b) +
  prior(normal(0, 1), class = b, coef = sex1) +
  # Standard deviations
  prior(
    student_t(7, 0, .5), class = sd, group = region
  ) +
  prior(
    student_t(7, 0, 1.5), 
    class = sd, group = country, coef = Intercept
  ) +
  prior(
    student_t(7, 0, .5), class = sd, group = region
  ) +
  prior(
    student_t(7, 0, 1.5), 
    class = sd, resp = val, group = country, coef = Intercept
  ) +
  # Correlations
  prior(lkj(2), class = cor, group = country) +
  prior(lkj(2), class = cor, group = region)

# Compile model separately for each outcome to give independent default priors
fits_2c <- dat %>%
  group_by(cause) %>% 
  summarise(
    fit = list(
      brm(
        formula = bf_2c, 
        data = cur_data_all(),
        prior = p,
        sample_prior = "yes",
        chains = hmc$chains, 
        cores = hmc$cores, 
        threads = hmc$threads,
        iter = hmc$iter, 
        warmup = hmc$warmup, 
        refresh = hmc$refresh,
        control = list(
          adapt_delta = hmc$adapt_delta, 
          max_treedepth = hmc$max_treedepth
        ),
        file = str_glue("output/brm-2c-{cur_group()}")
      )
    )
  )
```

@@

```{r}
f2d <- fits_2c %>% 
  mutate(
    out = 
      map(
        fit, 
        ~as_draws_df(., variable = "^b_|^sd_", regex = TRUE) %>% 
          summarise_draws(samples = length, default_convergence_measures())
      )
  ) %>% 
  select(-fit) %>% 
  unnest(out)
f2d %>%  
  kbl(
    caption = "HMC Diagnostics, Model 2c",
    digits = c(0,0,0,2,0,0)
  ) %>% 
  kable_paper(html_font = Font, full_width = FALSE) %>% 
  column_spec(
    4, 
    color = "white",
    background = spec_color(
      f2d$rhat, 
      direction = 1, 
      option = "C", 
      end = .7
    )
  ) %>% 
  scroll_box(height = "600px", width = "800px")
```

```{r}
tmp <- fits_2c %>% 
  mutate(
    out = map(
      fit, 
      ~pp_check(
        .x, 
        ndraws = 10, 
        type = "dens_overlay_grouped",
        group = "region",
        resp = "val", 
        newdata = .x$data
      ) + 
        facet_wrap("group", nrow = 1, scales = "free_y")
    )
  )
wrap_plots(tmp$out, nrow = 3) &
  scale_x_continuous(
    breaks = pretty_breaks(2),
    labels = function(x) percent(x/100, 1)
  )
```

@@

```{r}
tmp <- fits_2c %>% 
  mutate(
    out = map(
      fit, 
      ~as_draws_df(.x, variable = "^b_", regex = TRUE) %>% 
        summarise_draws(
          mean, quantile, rhat, 
          .args = list(probs = c(.025, .975))
        )
    )
  ) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  mutate(across(where(is.numeric), ~round(., 2))) %>% 
  mutate(
    result = str_glue(
      "b = {mean} ({`2.5%`}, {`97.5%`})"
    )
  ) %>% 
  rowwise() %>% 
  select(-c(mean, `2.5%`, `97.5%`, rhat)) %>% 
  pivot_wider(names_from = cause, values_from = result)
tmp %>%   
  kbl() %>% 
  kable_paper(html_font = Font) 
```

@@

```{r}
tmp <- fits_2c %>% 
  mutate(
    out = map(
      fit, 
      ~spread_draws(.x, b_i1_cw, r_region[region, term] | region) %>% 
        filter(term == "i1_cw") %>% 
        ungroup() %>% 
        select(-term) %>% 
        rename(Average = b_i1_cw) 
    )
  ) %>% 
  select(-fit) %>% 
  unnest(out)

names(tmp) <- str_replace(names(tmp), "\\.", " ")

tmp_text <- tmp %>% 
  group_by(cause) %>% 
  summarise(parameters(cur_data()[-c(1:3)], test = "pd")) %>% 
  rename(region = Parameter) %>% 
  mutate(is_average = region == "Average") %>% 
  mutate(region = if_else(region=="Average", "**Average**", region)) %>% 
  mutate(across(Median:CI_high, ~format(round(., 2), nsmall = 2)))

p_tmp <- tmp %>% 
  mutate(across(Africa:`Southern Asia`, ~.+Average)) %>% 
  pivot_longer(Average:`Southern Asia`, names_to = "region") %>% 
  mutate(region = if_else(region=="Average", "**Average**", region)) %>% 
  mutate(region = fct_relevel(factor(region), "**Average**")) %>% 
  mutate(cause = factor(cause)) %>% 
  mutate(is_average = region == "**Average**") %>% 
  ggplot(aes(value, region, fill = is_average, alpha = is_average)) +
  scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
  scale_alpha_manual(values = c(.4, .8)) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  scale_shape_manual(values = c(21, 19)) +
  scale_y_discrete(expand = expansion(c(0.01, .1))) +
  scale_x_continuous(
    "Magnitude of association between internet adoption and well-being", 
    breaks = pretty_breaks(), 
    expand = expansion(c(.1, .5))
  ) +
  stat_halfeye(
    point_interval = NULL, normalize = "panels", 
    height = .75, adjust = 1.5
  ) +
  stat_pointinterval(
    alpha = 1, .width = c(.9),
    interval_size = 1,
    point_size = 1.5,
    fill = "white",
    aes(shape = after_stat(xmin > 0 | xmax < 0)),
    position = position_nudge(0, -.025)
  ) +
  geom_text(
    data = tmp_text, alpha = 1, size = 2.75, hjust = 1, vjust = -0.2,
    aes(
      x = Inf,
      label = str_glue("{Median} [{CI_low}, {CI_high}]")
    )
  ) +
  facet_wrap("cause", nrow = 1, scales = "free_x") +
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_markdown(),
    legend.position = "none"
  )

(wrap_elements(grid::textGrob('Negative experiences\nTBD')) |
    wrap_elements(grid::textGrob('Positive experiences\nTBD')) |
    wrap_elements(grid::textGrob('Life satisfaction\nTBD'))) /
  p_tmp
```

@@

```{r}
tmp <- dat %>% 
  group_by(region, country, cause) %>% 
  summarise(
    internet = mean(internet, na.rm = TRUE),
    val = mean(val, na.rm = TRUE)
  ) 
tmp %>% 
  group_by(cause, region) %>% 
  summarise(tidy(lm(scale(val) ~ scale(internet), data = cur_data()))) %>% 
  filter(term != "(Intercept)") 
tmp %>% 
  ggplot(aes(internet, val)) +
  geom_point() +
  stat_smooth(method = "lm", se = F) +
  facet_grid(cause~region, scales = "free_y")

plot(conditional_effects(fits_2c$fit[[3]], "i1_cb"), points = TRUE)
x <- conditional_effects(fits_2c$fit[[3]], "i1_cb")[[1]]

x <- fits_2c$fit[[3]]
y <- fitted(x)
as_tibble(cbind(x$data, y)) %>% 
  arrange(desc(Estimate))
```

@@

```{r}
tmp <- fits_2c %>% 
  mutate(
    out = map(
      fit, 
      ~emtrends(.x, var = "i1_cw", by = c("sex"), at = list(age1=0, age2=0))
    )
  )
tmp$out[[1]] %>% summary
```

Calculate coefficients from contrast coded factors

```{r}
x <- fits_2c$fit[[1]]
y <- emtrends(x, var = "i1_cw", by = c("age", "sex"))
gather_emmeans_draws(y) %>% mean_qi()

contrasts(x$data$sex)
contrasts(x$data$age)
h <- c(
  `Female_10 to 14` = 
    "i1_cw + sex1:i1_cw*1 + age1:i1_cw*1 + age2:i1_cw*0 = 0",
  `Female_15 to 19` = 
    "i1_cw + sex1:i1_cw*1 + age1:i1_cw*0 + age2:i1_cw*1 = 0",
  `Female_20 to 24` = 
    "i1_cw + sex1:i1_cw*1 + age1:i1_cw*-1 + age2:i1_cw*-1 = 0",
  `Male_10 to 14` = 
    "i1_cw + sex1:i1_cw*1 + age1:i1_cw*1 + age2:i1_cw*0 = 0",
  `Male_15 to 19` = 
    "i1_cw + sex1:i1_cw*1 + age1:i1_cw*0 + age2:i1_cw*1 = 0",
  `Male_20 to 24` = 
    "i1_cw + sex1:i1_cw*1 + age1:i1_cw*-1 + age2:i1_cw*-1 = 0"
)
tmp_avg <- hypothesis(x, h)
tmp_region <- hypothesis(x, h, scope = "coef", group = "region")
```

```{r}
# Get some stuff and transform
get_draws <- function(x) {
  draws_region <- spread_draws(
    x, 
    b_i1_cw, `b_sex1:i1_cw`, `b_age1:i1_cw`, `b_age2:i1_cw`,
    r_region[region, term] | term
  ) %>% 
    mutate(
      `10 to 14` = b_i1_cw + i1_cw + 
        `age1:i1_cw`*1 + `b_age1:i1_cw`*1 +
        `age2:i1_cw`*0 + `b_age2:i1_cw`*0,
      `15 to 19` = b_i1_cw + i1_cw + 
        `age1:i1_cw`*0 + `b_age1:i1_cw`*0 +
        `age2:i1_cw`*1 + `b_age2:i1_cw`*1,
      `20 to 24` = b_i1_cw + i1_cw + 
        `age1:i1_cw`*-1 + `b_age1:i1_cw`*-1 +
        `age2:i1_cw`*-1 + `b_age2:i1_cw`*-1,
      Female = b_i1_cw + i1_cw + `sex1:i1_cw`*1 + `b_sex1:i1_cw`*1,
      Male = b_i1_cw + i1_cw + `sex1:i1_cw`*-1 + `b_sex1:i1_cw`*-1,
      Age = `20 to 24` - `10 to 14`,
      Sex = Female - Male
    ) %>% 
    select(region, `10 to 14`:Sex)

  draws_avg <- spread_draws(
    x, 
    b_i1_cw, `b_sex1:i1_cw`, `b_age1:i1_cw`, `b_age2:i1_cw`,
  ) %>% 
    mutate(
      `10 to 14` = b_i1_cw + `b_age1:i1_cw`*1 + `b_age2:i1_cw`*0,
      `15 to 19` = b_i1_cw + `b_age1:i1_cw`*0 + `b_age2:i1_cw`*1,
      `20 to 24` = b_i1_cw + `b_age1:i1_cw`*-1 + `b_age2:i1_cw`*-1,
      Female = b_i1_cw + `b_sex1:i1_cw`*1,
      Male = b_i1_cw + `b_sex1:i1_cw`*-1,
      Age = `20 to 24` - `10 to 14`,
      Sex = Female - Male
    ) %>% 
    select(`10 to 14`:Sex) %>% 
    mutate(region = "**Average**")

@@

draws <- fits_2c %>% 
  mutate(out = map(fit, get_draws)) %>% 
  select(-fit) %>% 
  unnest(out)

# Summaries of differences
draws_sum <- draws %>% 
  select(cause, region, Age, Sex) %>% 
  group_by(cause, region) %>% 
  summarise(
    describe_posterior(
      cur_data(), centrality = "mean", test = "pd"
    )
  ) %>% 
  rename(panel = Parameter) %>% 
  mutate(across(where(is.numeric), ~round(., 2)))
